Discourse and Deforestation in the Amazon - Silva and Sposito

### 2021-09-30 Trabalho com o Liviao.Rmd
Deleted package structure

# Amazon name is refreed to 1064 times (ranks around 950).

dp1 <- dfm_wordstem(dp1, language = "portuguese")

@@

>>>>

dp2 <- dfm_wordstem(dp1, language = "portuguese")

@@

# Amazon name is refreed to 1064 times (ranks around 950). 
# plotting occurences across time

library(tidyverse)
library(ggplot2)
library(reshape2)
library(scales)

dat <- as.data.frame(Discursos_Presidenciais)

ggplot(dat %>% group_by(date, label=TRUE)) %>%
         summarise(A = sum(grepl("Amazônia"),
                   B = sum(grepl("desmatamento")))) %>%
         melt(id.var="date") +
       aes(date) +
  geom_line()
